\documentclass[12pt]{article}
\textwidth=7in
\textheight=9.5in
\topmargin=-1in
\headheight=0in
\headsep=.5in
\hoffset  -.85in

\pagestyle{empty}
\begin{document}

\begin{center}
{\bf Astronomy 150 -- The Planets \\  Fall 2013 Syllabus}
\end{center}

\setlength{\unitlength}{1in}

\begin{picture}(6,.1) 
\put(0,0) {\line(1,0){6.25}}         
\end{picture}\\

\noindent
{\bf Teaching Assistant:} Brett Morris\\
{\bf Email:} bmmorris@u.washington.edu\\
{\bf My Office:} PAB B337\\
{\bf Office Hours:} Monday and Wednesday from 3:00-4:00pm, or by appointment\\
{\bf Course Website:} astro150.org\\
{\bf Section Room:} \textit{Section AI}: PAA A210;  \textit{Section AE}: PAA A216 \\
%\begin{center}

\begin{picture}(6,.1) 
\put(0,0) {\line(1,0){6.25}}         
\end{picture}\\

\noindent
Welcome to AST 150! Here are a few reiterations of Dr. Smith's syllabus pertaining to section. \\
%\end{center}


\noindent
{\bf Office Hours: }  
My office (B337) is in the Physics and Astronomy Building (PAB) on the third floor,
look for the ``B. Morris'' tag next to my door. You can find me in my office on
Monday and Wednesday from 3:00-4:00pm, or if those times don't work for you, 
send me an email and we'll find one that works. 
Office hours are your chance to get help with assignments, ask questions before
exams, and learn more about astronomy. If you can not attend the hours at the times posted 
above, contact me and we will set up a time that works for you. Don't
wait until the day before the test to ask a question -- come to office hours!\\

\noindent
{\bf Section Work: }
From Dr. Smith's syllabus: ``\textit{No late work will be accepted in section. 
Missing a lab will result in zero credit for that lab.}'' Don't forget that your work in 
section counts for 30\% of your grade in this course (more than either the mid-term
or the final).\\


\end{document}
\noindent
{\bf Important Dates}
\begin{center}
    \begin{tabular}{c|c|c}
    Exam & Review Date & Exam Date \\ \hline
    Midterm 1 & Sept 28 & Oct 1 \\
    Midterm 2 & Oct 16 & Oct 22 \\
    Midterm 3 & Nov 15 & Nov 16\\
    Final & Dec 15 or 16 & Dec 17 (8-10am)\\
    \end{tabular}\\
\end{center}